---
title: "smt package vignette"
author: "Sheng Liu"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style




## msd method
```{r,eval=FALSE}

folder=system.file("extdata",package="smt")
trackll=readDiatrack(folder)

# merged trackll
trackll.merge=readDiatrack(folder,T)

track=trackll[[1]][[1]]

squareDisp(track)

squareDisp(track,2)

msd.track(track,2)




# length of all tracks in first file
sapply(trackll[[1]],function(x) dim(x)[1])



track27=trackll[[1]][[27]]

squareDisp(track27,5)

msd.track(track27,5)

# not just mean at dt=5
x=sapply(squareDisp(track27,5),function(x){mean(x$square.disp,na.rm=T)})

mean(x)

y=sapply(squareDisp(track27,5),function(x){(x$square.disp)})
> mean(y,na.rm=T)
[1] 0.1011864

do.call(rbind,squareDisp(track27,5))

do.call(rbind,squareDisp(track27,5))$square.disp


plot(track27$x,track27$y,type="l")



```













## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
